%!TEX TS-program = xelatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Kye}{Burchard}{kyeb@mit.edu | \href{https://github.com/kyeb}{github.com/kyeb} | (406) 217-6239 | \href{https://kyeburchard.com}{kyeburchard.com}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

\newsection{MIT}\descript{| SB Electrical Engineering and Computer Science}\hfill \location{2017 - 2021}\\
GPA: 4.9\\
\sectionsep

% \newsection{Great Falls High School}\descript{| Great Falls, Montana}\hfill \location{2013 - 2017}\\
% GPA: 4.0 \textbar{} Rank: 1/298 \textbar{} ACT: 35 \textbar{} National Merit Scholar\\
% \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\newsection{Stripe}\descript{| Software Engineering Intern}\hfill \location{May - Aug. 2020}
\begin{tightemize}
	\item Building infrastructure to improve performance of the Stripe dashboard, a massive React/Redux app
\end{tightemize}
\sectionsep

\newsection{web.lab}\descript{| Operations Chair}\hfill \location{Jan. 2020}
\begin{tightemize}
    \item Coordinated logistics, course staff, and delivered 2 lectures for 200 person IAP class
\end{tightemize}
\sectionsep

\newsection{Microsoft Garage}\descript{| Software Engineering Intern}\hfill \location{May - Aug. 2019}
\begin{tightemize}
    \item Designed and implemented a modular, scalable data architecture for an independent intern project
    % \item Initiated and led a reorganization of team's Git workflow
    \item Facilitated communication across 4 disparate dev teams to produce a working prototype
\end{tightemize}
\sectionsep

\newsection{MIT Media Lab}\descript{| Undergraduate Researcher}\hfill \location{May - Aug. 2018}
\begin{tightemize}
	\item Designed algorithm and data pipeline to improve location detection for Rhythm Badges project
	% \item Developed a full data processing pipeline, from raw output to analyzable dataframes, leveraging multi-core processing for efficiency
\end{tightemize}
\sectionsep

\newsection{HackMIT}\descript{| Logistics Head 2019, Dev \& Corporate Relations 2018}\hfill \location{April 2018 – Sept. 2019}
\begin{tightemize}
    \item Heading up a 12-person logistics team to plan and execute MIT's largest hackathon 
    \item Designed layouts, schedules, and staffing for a 1,200-person event over 3 days
\end{tightemize}
\sectionsep

\newsection{Maseeh Hall}\descript{| President 2019, Treasurer 2018, WebTech Chair 2018-2020}\hfill \location{Jan. 2018 – May 2020}
\begin{tightemize}
    \item Led largest dorm at MIT in reviving clubs and committees, resulting in a 20\% improvement in retention
\end{tightemize}
\sectionsep

\newsection{Other}\descript{}\hfill \location{}
\begin{tightemize}
    \item \custombold{CLICK} Startup focusing on empowering influencers to be more productive
    \item \custombold{SIPB} Contributing member to MIT's volunteer student computing group
    \item \custombold{6.08} Lab assistant for Intro to EECS via Interconnected Embedded Systems
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\raggedright

\newsection{\large{Politichat}}
\descript{| React, Express, socket.io, Jitsi}\hfill \location{\href{https://politi.chat}{politi.chat}}\\
Startup helping campaigns in the age of COVID-19 with a replacement for 1-on-1 conversations with candidates.
\newline
Project for CS91r at Harvard and part of the HCS Builders Incubation Program during summer 2020.
\sectionsep

\newsection{\large{StreetSmarts}}
\descript{| C++, Python, SQL}\hfill
\location{\href{https://lrylander.github.io/StreetSmarts}{lrylander.github.io/StreetSmarts}}\\
A smart street lamp system for emergency responders, leveraging real-time optimal routing and cloud-based synchronization. Final project for 6.08\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Coursework
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\begin{tabular}{ l l }

\newsection{\large{Spring 2020}} & 6.858 Computer Security, 18.05 Probability \& Statistics, CS91r Political Tech (Harvard) \\

\newsection{\large{Fall 2019}} &6.172 Performance Engineering, 6.034 Artificial Intellligence, 18.06 Linear Algebra \\

\newsection{\large{Spring 2019}} &6.033 Computer Systems Engineering, 6.002 Circuits, 6.036 Machine Learning\\

% \newsection{\large{Fall 2018}} &6.004 Computation Structures, 6.08 Intro to Embedded Systems, 6.006 Intro to Algorithms \\

\end{tabular}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{tabular}{ l l }
	\descript{Advanced}      & {\location{Python, Linux, JavaScript, C}} \\
	\descript{Knowledgeable} & {\location{React, Typescript, HTML/CSS, C++, Git, \LaTeX, C\#, Vim}} \\
	\descript{Exploring}     & {\location{Ruby, Rust, Bash, Redux}} \\
\end{tabular}
\sectionsep
\end{document}
